Post CMOS technologies: An Overview and Analysis

### 2025-06-03 Paper.tex
memristor section

@@

>>>>

\subsection{Personal Thoughts}
Overall CNFETs seem like a very promising area where there could be 
a lot of development. Since it doesn't deviate signficantly from 
traditional transistors it can be implemented into already made 
computing schemes making it more appealing for companies to invest 
in. It is much more likely for top fabrication companies like 
TSMC or Intel to look into CNFETs than some other technologies
that present completely new computing paradigms. The progress made in 
CNFETs has also been extremely promising as demonstrated by MIT's 
RV16X-NANO computer. The milestone to already have demonstrated 
such funcionality proves that this is a technology that is really 
feasible for the future. Graphene is also an area that has a good 
amount of research going into it so carbon nanotubes in general 
are sure to get more attention.

With new chips there is a greater emphasis on chiplet technology 
as well as 3D integration. Again, CNFETs look very promising in that
area. Along with that, the medical industry is also constantly looking 
for flexible devices that can better interact with the human body 
which is another area where CNFETs shine in.

Though there are still some big hurdles to overcome in manufacturing 
CNFETs at large scales and reliably I believe with just a few more 
breakthroughs they can become quite mainstream where large amounts 
of investments will be poured into CNFETs and accelerate their development 
greatly.

@@

\subsection{Threshold Logic Gate}
A threshold logic gate is a gate that outputs a high signal if 
an input signal surpasses a certain threshold and outputs low 
otherwise. To give an example simply, imagine the input had a range 
of voltages from 0-9 and there is a threshold voltage of 5. Any
input voltage above high will output a binary high signal from the 
gate and any voltage below will output a low signal. A TLG 
is oftentimes also used to analyze a weighted sum from its inputs 
and see if that is above the threshold.

With these characteristics a TLG can implement any linearly separable
function. This means that for a given function, there exists a 
dividing line (or hyperplane in higher dimensions) that would 
separate all input combinations to one of two distinct output 
groups.

This also means that a single TLG can implement a boolean function 
that would require multiple logic gates to realize. For example, a 
majority gate would require at least 4 NAND gates to be realized in 
traditional CMOS design while it can be implemented in just one TLG.

\subsubsection{Memristor-Based Threshold Logic Gate}
da
